Scheeper's Meager-NWD Game and the Menger Game

### 2014-08-25 phd/dissertation/_raw_chapter6.tex
Name and camelCase based game commands/definitions

\input{../header.tex}

\begin{document}

  \centerline{Menger}

  \begin{definition}
    $X$ is \textbf{Menger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist finite subcollections $\mathcal{F}_n \subseteq \mathcal{U}_n$ such that $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{definition}

  \begin{proposition}
    $\sigma$-compact $\Rightarrow$ Menger $\Rightarrow$ Lindelof
  \end{proposition}

  \begin{definition}
    In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $F$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$. $F$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{definition}

  \begin{theorem}
    $X$ is Menger if and only if $C \not\win \mengame{X}$.
  \end{theorem}

@@

    First, suppose $X$ wasn't Menger. Then there would exist open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ of $X$ such that for any choice of finite subcollections $\mathcal{F}_n\subseteq\mathcal{U}_n$, $\bigcup_{n<\omega} \mathcal{F}_n$ isn't a cover of $X$. Thus $C\prewin\mengame{X} \Rightarrow S \not\win\mengame{X}$.

    Now, assume $X$ is Menger, and consider a strategy for $C$ in $\mengame{X}$.

@@

  \begin{proposition}
    $X$ is compact if and only if $F \tactwin \mengame{X}$ if and only if $F \ktactwin{k} \mengame{X}$
  \end{proposition}

@@

  \begin{proposition}
    If $X$ is $\sigma$-compact then $F \markwin \mengame{X}$
  \end{proposition}

@@

  \begin{theorem}
  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \mengame{X}$ if and only if $F \kmarkwin{2} \mengame{X}$.
  \end{theorem}

@@

  \begin{example}
    $F \win \mengame{\oneptlind{\omega_1}}$ but $F \not\markwin \mengame{\oneptlind{\omega_1}}$.
  \end{example}

@@

  % \begin{definition}
  %   A space $X$ is $H$-closed if for every open cover of $X$, there exists a finite subset of the cover whose union is dense in $X$.
  % \end{definition}

  % \begin{proposition}
  %   For regular spaces, $X$ is $H$-closed if and only if $X$ is compact.
  % \end{proposition}

  % \begin{proof}
  %   The backward implication is trivial, so let $X$ be $H$-closed. For any open cover $\mc U$ of $X$ and point $x\in X$, choose $x\in V_x\subseteq \cl{V_x}\subseteq U_x\in \mc U$. Then if $\mc F = \{V_{x_i}:i<n\}$ is a finite subset of $\mc V=\{V_x:x\in X\}$ with dense union in $X$, then $\mc G = \{U_{x_i}:i<n\}\subseteq \mc U$ is a finite subcover of $X$.
  % \end{proof}

  \begin{definition}
    A set $R\subseteq X$ is relatively compact to the topological space $X$ if for every open cover of the entire space $X$, there is a finite subcover of the set $R$.
  \end{definition}

  \begin{proposition}
    If $X$ is regular, then $Y$ is relatively compact if and only if $\cl{Y}$ is compact.
  \end{proposition}

@@

  \begin{lemma}
    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
      \[
        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
    it follows that $R_n$ is relatively compact to $X$, and $\bigcup_{n<\omega} R_n = X$.
  \end{lemma}

@@

  \begin{corollary}
    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
  \end{corollary}

  \begin{corollary}
    For regular spaces $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \markwin \mengame{X}$
      \end{enumerate}
  \end{corollary}

  \begin{theorem}
    For second-countable $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \win \mengame{X}$
        \item $F\markwin \mengame{X}$
      \end{enumerate}
  \end{theorem}

@@

  \begin{corollary}
    For metric spaces $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \win \mengame{X}$
        \item $F \markwin \mengame{X}$
      \end{enumerate}
  \end{corollary}

  \begin{example}
  Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed. This space is a non-regular example where $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$, that is, $R$ is not $\sigma$-(relatively compact).
  \end{example}

@@

  We define a new property ``\scish'' to describe a sufficient condition for $F \kmarkwin{2}\mengame{X}$.

  \begin{definition}
    Let $\mc U$ be a cover of $X$. We say $C\subseteq X$ is $\mc U$-compact if there exists a finite subcover of $\mc U$ which covers $C$.

    We say $X$ is \scish~if there exist functions $r_{\mc V}:X\to\omega$ for each open cover $\mc V$ of $X$ such that both of the following sets are $\mc V$-compact for all open covers $\mc U$, $\mc V$ and $n<\omega$:
      \[
        c(\mc V,n)=\{ x\in X : r_{\mc V}(x)\leq n\}
      \]
      \[
        p(\mc U,\mc V)=\{ x\in X : 0<r_{\mc U}(x)<r_{\mc V}(x)\}
      \]
  \end{definition}

  \begin{definition}
    For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$. If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\alcomp g$).
  \end{definition}

  \begin{lemma}\label{kunlem}
    For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \alcomp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals. In addition, the range of each $f_\alpha$ is co-infinite.
  \end{lemma}

@@

  \begin{theorem}
    If $X$ is \scish, then $F \kmarkwin{2}\mengame{X}$.
  \end{theorem}

@@

  \begin{corollary}
    $F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$
  \end{corollary}

  \begin{definition} 
    The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\alcomp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
  \end{definition}

  \begin{proposition}
    $\neg S(\kappa,\omega,\omega)$ for $\kappa>2^\omega$
  \end{proposition}

@@

  \begin{corollary}
    $S(\kappa,\omega,\omega)$ implies $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$.
  \end{corollary}

  \begin{definition}
    A finite partial function $p$ from $A$ to $B$ has a domain which is a finite subset of $A$ and a range which is a finite subset of $B$. Let the set of all finite partial functions from $A$ to $B$ be denoted by $Fn(A,B)$.

    Then let $Fn^2(\mc A,B)\subset Fn(\mc A,Fn(\bigcup \mc A,B))$ such that for each $p\in Fn^2(\mc A,B)$, $p(A)=p_A\in Fn(A,B)$.
  \end{definition}

  \begin{definition}
    Let $\pok\subset Fn^2([\kappa]^\omega,\omega)$ be such that each $p_A$ is injective, and give it the partial order $\leq$ defined by $q\leq p$ if and only if:
          \begin{itemize}
            \item $\dom(q)\supseteq\dom(p)$
            \item For each $A\in\dom(p)$, $q_A\supseteq p_A$
            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$. That is, for $\alpha\in A\cap B$ 
              \[
                \alpha\in\dom(q_A)\setminus(\dom(p_A)\cup\dom(p_B))
                \Rightarrow
                \alpha\in\dom(q_B) \text{ and } q_A(x)=q_B(x)
              \]
          \end{itemize}
  \end{definition}

  \begin{lemma}
    $\pok$ has property $K$ (and thus is c.c.c.). That is, let $P\subseteq\pok$ be uncountable: there is an uncountable $Q\subseteq P$ such that points in $Q$ are pairwise compatible.
  \end{lemma}

@@

  \begin{corollary}
    For each $\kappa$, $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with ZFC.
  \end{corollary}

  \begin{definition}
    A space suggested by G: Give $\kappa^\sharp=(\kappa\times\oneptlind\kappa)\cup\{\infty\}$ the topology where $\{\alpha\}\times\kappa^\sharp$ is an open copy of $\oneptlind{\kappa}$, and neighborhoods of $\infty$ contain a set of the form $\kappa^\sharp\setminus(A\times\oneptlind\kappa)$ for some $A\in[\kappa]^\omega$.
  \end{definition}

  \begin{theorem}
    $F\kmarkwin{2}\mengame{\omega_1^\sharp}$
  \end{theorem}

  \begin{proof}
    Let $f_\alpha:\alpha\to\omega$ witness $S(\omega_1,\omega,\omega)$ for limit ordinals $\alpha<\omega_1$. Also note that there is a bijection $e:\omega_1\to[\omega_1]^{<\omega}$ such that $e\rest\alpha:\alpha\to[\alpha]^{<\omega}$ is also a bijection for each limit ordinal $\alpha<\omega_1$.

    We define the finite set $F(\alpha_n,\alpha_{n+1},n+1)$ to contain $e(\beta)$ for each $\beta<\alpha_n\cap\alpha_{n+1}$ such that either $f_{\alpha_{n+1}}(\beta)\leq n$ or $f_{\alpha_{n}}(\beta)\not=f_{\alpha_{n+1}}(\beta)$.

    If $\alpha_n<\omega_1$ for all $n<\omega$ with $\alpha=\min\{\alpha_{n+1}:n<\omega\}$ and $G\in[\alpha]^{<\omega}$, note that for each $\beta<\alpha$, either $f_{\alpha_n}(\beta)=N$ always, or $f_{\alpha_n}(\beta)\not=f_{\alpha_{n+1}}(\beta)$ for some $n$. Either way, $e(\beta)\subseteq F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$, and thus every finite subset of $\alpha$ is contained in some $F(\alpha_n,\alpha_{n+1},n+1)$.

    If we let $R(\alpha)=\omega_1^\sharp\setminus(A\times\oneptlind\omega_1)$ and $U(\gamma,\alpha)=\{\gamma\}\times(\oneptlind\omega_1\setminus\alpha)$, then any open cover of $\omega_1^\sharp$ may be refined to be of the form $\mc U_\alpha = \{R(\alpha)\}\cup\{U(\gamma,\alpha):\gamma<\alpha\}\cup\{\{(\gamma,\beta)\}:\gamma,\beta<\alpha\}$ for some limit $\alpha$.

    Without loss of generality assume $\pl C$ plays only covers of the form $\mc U_\alpha$ for limit $\alpha$. Then we may define the $2$-Markov strategy $\sigma(\mc U_{\alpha_n},\mc U_{\alpha_{n+1}},n+1)$ to cover the sets:
      \[
        R(\alpha_{n+1})
      \]
      \[
        \bigcup \{U(\gamma,\alpha_{n+1}) : \gamma \in F(\alpha_n,\alpha_{n+1},n+1) \}
      \]
      \[
        \{(\gamma,\delta): \gamma,\delta\in F(\alpha_n,\alpha_{n+1},n+1)\}
      \]

    Let $\mc U_{\alpha_0},\mc U_{\alpha_1},\dots$ be an attack by $\pl C$, $\alpha=\min\{\alpha_{n+1}:n<\omega\}$ and $\alpha'=\sup\{\alpha_{n+1}:n<\omega\}$. Since $\infty\in R(\alpha_0)$ always, first consider $(\gamma,\infty)$ for $\gamma<\omega_1$. If $\gamma\geq\alpha_{n+1}$ for some $n$, then $(\gamma,\infty)\in R(\alpha_{n+1})$. Otherwise, $\gamma<\alpha$, but then $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ and $(\gamma,\infty)\in U(\gamma,\alpha_{n+1})$.

    Lastly consider $(\gamma,\delta)$ for $\gamma,\delta<\omega_1$. If $\gamma\geq\alpha_{n+1}$ for some $n$, then $(\gamma,\delta)\in R(\alpha_{n+1})$.

    Otherwise, $\gamma<\alpha$. If $\delta\geq \alpha'$, then as $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ we see $(\gamma,\delta)\in U(\gamma,\alpha_{n+1})$. If $\delta<\alpha$, then $\{\gamma,\delta\}\subseteq F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ and $(\gamma,\delta)$ is covered. The final case is when $\alpha\leq\delta<\alpha'$.

    (STILL MISSING STUFF)

    % If $\alpha_{n+1}=\beta$ is fixed for $n\in W\in[\omega]^\omega$, observe that $f_{\alpha_{n+1}}(\gamma)=f_\beta(\gamma)=N$ for all $n\in W$, and thus $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n\in W\setminus N$. Thus $(\gamma,\delta)\in U(\gamma,\alpha)$ is covered.
  \end{proof}

  % \begin{lemma}
  %   For each infinite cardinal $\kappa$, the sentence $S(\kappa,\omega,\omega)$ implies there exists a function $F:[\kappa]^\omega\times[\kappa]^\omega\times\omega\to [\kappa]^{<\omega}$ such that for any choice of $A_n\in[\omega]^\omega$ and $G\in[\bigcap_{m<\omega}\bigcup_{m\leq n<\omega} A_{n+1}]^{<\omega}$, there exists an $n<\omega$ with $G\subseteq F(A_n,A_{n+1},n+1)$.
  % \end{lemma}

  % \begin{proof}
  %   Let $\Lim([\kappa]^\omega)\subseteq[\kappa]^\omega$ denote the countable subsets of $\kappa$ for which if a set contains $\alpha+n$, then it contains $\alpha+m$ for all $m<\omega$.

  %   Let $e:[\kappa]^{<\omega}\to\kappa$ be a bijection such that for every $A\in\Lim([\kappa]^\omega)$, $e\rest [A]^{<\omega}:[A]^{<\omega}\to A$ is a bijection.

  %   Then for $A,B\in\Lim([\kappa]^\omega)$ let $F(A,B,n+1)$ contain all $G\in[B]^{<\omega}$ satsifying $f_{B}(e(G))\leq n$, and also contain all $G\in[A\cap B]^{<\omega}$ satisfying $f_{A}(e(G))\not= f_{B}(e(G))$.

  %   Fix arbitrary $A_n\in[\omega]^\omega$ and $G\in[\bigcap_{m<\omega}\bigcup_{m\leq n<\omega} A_{n+1}]^{<\omega}$.
  % \end{proof}

  % \begin{theorem}
  %   $F\kmarkwin{2}\mengame{\omega_1^\sharp}$
  % \end{theorem}

  % \begin{proof}
  %   Let $f_A$ witness $S(\kappa,\omega,\omega)$ for each $A<[\kappa]^{\omega}$.

  %   Let $R(A)=\kappa^\sharp\setminus(A\times\oneptlind\kappa)$. Let $U(\gamma,A)=\{\gamma\}\times(\oneptlind{\kappa}\setminus A)$. Then note that every open cover has a pairwise disjoint open refinement of the form 
  %     \[
  %       \mc U_A = 
  %       \{R(A)\}\cup\{U(\gamma,A):\gamma\in A\}\cup\{\{(\gamma,\beta)\}:\gamma,\beta\in A\}
  %     \]
  %   Assume without loss of generality that all covers are of the form $\mc U_A$.

  %   % Rough idea: Let $\mc U_\alpha$ cover...

  %   % Let $\sigma(\mc U,\mc V,n+1)$ be a $2$-mark.

  %   % Let $F(\alpha_n,\alpha_{n+1},n+1) = \{\alpha<\alpha_n\cap\alpha_{n+1}:\sigma(\mc U_{\alpha_n},\mc U_{\alpha_{n+1}},n+1)$ covers $(\alpha,\beta)$ or $(\beta,\alpha)$ for some $\beta\}$.

  %   % Claim: It is not true that for all $\alpha,\beta<\alpha_0<\alpha_1<\dots$ there exists $n<\omega$ with $\alpha,\beta\in F(\alpha_n,\alpha_{n+1},n+1)$.

  %   % If so, then choose $\alpha,\beta<\alpha_0<\alpha_1<\dots$ such that $\alpha,\beta\not\in\bigcap_{n<\omega}F(\alpha_n,\alpha_{n+1},n+1)$. Then $\sigma$ covers neither $(\alpha,\beta)$ or $(\beta,\alpha)$ in response to the attack $\mc U_{\alpha_0},\mc U_{\alpha_1},\dots$
  % \end{proof}

@@

  Besides various limited information characterizations of $\mengame{X}$, there are other interesting covering properties between $\sigma$-(relatively compact) and Menger.

  \begin{definition}
    A colleciton of subsets of a space $X$ is (\textbf{really}) \textbf{ample} if has a finite subcover for each (relatively) compact subset of $X$.
  \end{definition}

  \begin{proposition}
    Every ample cover of a regular space $X$ is really ample.
  \end{proposition}

@@

  \begin{example}
    Let the real numbers $R$ be given the topology generated by open intervals with countable sets removed. $R$ is not relatively Alster and $F\win\mengame{R}$. If $S(2^\omega,\omega,\omega)$ holds, then $F\kmarkwin{2}\mengame{R}$.
  \end{example}

@@

    It was proven earlier that $F\win\mengame{R}$. Assuming $S(2^\omega,\omega,\omega)$, we construct a $2$-Mark\"ov strategy by first defining the following:
      \begin{itemize}
        \item Let $z_n$ enumerate the integers for $n<\omega$.
        \item For each open cover $\mc V$ of $R$, let $A(\mc V)$ be a countable set such that $[z_n,z_n+1)\setminus A(V)$ is $\mc V$-compact for each $n<\omega$.
        \item Let $f_A:A\to\omega$ for $A\subseteq R$ witness $S(2^\omega,\omega,\omega)$.
      \end{itemize}

@@

  \begin{definition}
    A space $X$ is \textbf{Hurewicz} if for each sequence of open covers $\mc U_n$, there are $\mc F_n \in [\mc U_n]^{<\omega}$ such that $X=\bigcup_{m<\omega}\bigcap_{m\leq n<\omega}\cup\mc F_n$.
  \end{definition}

  % Probably no good.
  % \begin{definition}
  %   A $\gamma$-cover $\mc U$ of $X$ is a countable cover such that each $x\in X$ is contained in all but finite members of $\mc U$.

  %   A $\gamma_\infty$-cover is an infinite $\gamma$-cover. 
  % \end{definition}

  % \begin{definition}
  %   A space $X$ is \textbf{Hurewicz} if and only if for each sequence $\mc U_n$ of $\gamma_\infty$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that either $\bigcup_{n<\omega} \mc F_n$ is a $\gamma_\infty$-cover, or $\mc F_N$ is a cover for some $N$.
  % \end{definition}

  % \begin{proposition}
  %   A space $X$ is Hurewicz if and only if for each sequence $\mc U_n$ of $\gamma$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover.
  % \end{proposition}

  % \begin{proof}
  %   Suppose $X$ is Hurewicz. For each sequence $\mc U_n$ of $\gamma$-covers, either:
  %     \begin{itemize}
  %       \item Each $\mc U_n$ is a $\gamma_\infty$-cover as well. Apply Hurewicz to find $\mc F_n$ such that either $\bigcup_{n<\omega} \mc F_n$ is a $\gamma_\infty$-cover (and thus a $\gamma$-cover) or else $\mc F_N$ is a cover for some $N$, so letting $\mc F_n'=\emptyset$ for $n\not=N$ and $\mc F_N'=\mc F_N$ yields the $\gamma$-cover $\bigcup_{n<\omega} \mc F_n'=\mc F_n$.
  %       \item Some $U_N$ is not a $\gamma_\infty$-cover as it is finite. Let $\mc F_n'=\emptyset$ for $n\not=N$ and $\mc F_N=\mc U_N$ to yield the $\gamma$-cover $\bigcup_{n<\omega} \mc F_n=\mc U_n$.
  %     \end{itemize}

  %   Suppose for each sequence $\mc U_n$ of $\gamma$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover. Then for each sequence $\mc U_n$ of $\gamma_\infty$-covers, let $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover. We are now done, unless $\bigcup_{n<\omega} \mc F_n$ is finite.
  % \end{proof}

@@

  \begin{definition}
    The \textbf{filling game} $\fillgame{J}$ on an ideal $J$ proceeds as follows: player $M$ chooses $M_0 \in \<J\>$, the $\sigma$-completion of $J$, in the initial round, followed by $N$ choosing $N_0\in J$. In round $n+1$, player $M$ chooses $M_{n+1}$ where $M_n\subseteq M_{n+1}\in\<J\>$, and player $N$ replies with $N_{n+1}\in J$. Player $N$ wins the game if $\bigcup_{n<\omega} N_n \supseteq \bigcup_{n<\omega} M_n$. (The sets in $J$ and $\<J\>$ are thought of as nowhere-dense and meager sets, respectively.)

    The \textbf{strict filling game} $\sfillgame{J}$ proceeds analogously, with the added requirement that $M_n\subsetneq M_{n+1}$. This game has been studied by Scheepers.
  \end{definition}

  \begin{theorem}
    $N\ktactwin{2}\sfillgame{J} \Rightarrow N\kmarkwin{2}\fillgame{J}$
  \end{theorem}

@@

    We define a $2$-Markov strategy $\tau$ for $F$ in $\fillgame{\kappa}$ as follows:

@@

  \begin{example}
    There is a free ideal $J$ such that $N\not\ktactwin{2}\sfillgame{J}$ but $N\kmarkwin{2}\fillgame{J}$.
  \end{example}

@@

    Certainly, if $J$ is the collection of nowhere dense subsets of $A\cup V$, then $F\kmarkwin{2}\fillgame{J}$. In fact, since $A\cup V$ is meager, $F\prewin\fillgame{J}$.

>>>>

%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

\chapter{Menger Game}

Results pertaining to the Menger game characterizing the Menger property.

\section{cut-and-paste}

  \begin{defn}
    $X$ is \textbf{Menger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist finite subcollections $\mathcal{F}_n \subseteq \mathcal{U}_n$ such that $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{defn}

  \begin{prop}
    $\sigma$-compact $\Rightarrow$ Menger $\Rightarrow$ Lindelof
  \end{prop}

  \begin{defn}
    In the two-player game $\menGame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $F$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$. $F$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{defn}

  \begin{thm}
    $X$ is Menger if and only if $C \not\win \menGame{X}$.
  \end{thm}

@@

    First, suppose $X$ wasn't Menger. Then there would exist open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ of $X$ such that for any choice of finite subcollections $\mathcal{F}_n\subseteq\mathcal{U}_n$, $\bigcup_{n<\omega} \mathcal{F}_n$ isn't a cover of $X$. Thus $C\prewin\menGame{X} \Rightarrow S \not\win\menGame{X}$.

    Now, assume $X$ is Menger, and consider a strategy for $C$ in $\menGame{X}$.

@@

  \begin{prop}
    $X$ is compact if and only if $F \tactwin \menGame{X}$ if and only if $F \ktactwin{k} \menGame{X}$
  \end{prop}

@@

  \begin{prop}
    If $X$ is $\sigma$-compact then $F \markwin \menGame{X}$
  \end{prop}

@@

  \begin{thm}
  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \menGame{X}$ if and only if $F \kmarkwin{2} \menGame{X}$.
  \end{thm}

@@

  \begin{ex}
    $F \win \menGame{\oneptlind{\omega_1}}$ but $F \not\markwin \menGame{\oneptlind{\omega_1}}$.
  \end{ex}

@@

  \begin{defn}
    A set $R\subseteq X$ is relatively compact to the topological space $X$ if for every open cover of the entire space $X$, there is a finite subcover of the set $R$.
  \end{defn}

  \begin{prop}
    If $X$ is regular, then $Y$ is relatively compact if and only if $\cl{Y}$ is compact.
  \end{prop}

@@

  \begin{lem}
    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\menGame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
      \[
        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
    it follows that $R_n$ is relatively compact to $X$, and $\bigcup_{n<\omega} R_n = X$.
  \end{lem}

@@

  \begin{cor}
    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \menGame{X}$.
  \end{cor}

  \begin{cor}
    For regular spaces $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \markwin \menGame{X}$
      \end{enumerate}
  \end{cor}

  \begin{thm}
    For second-countable $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \win \menGame{X}$
        \item $F\markwin \menGame{X}$
      \end{enumerate}
  \end{thm}

@@

  \begin{cor}
    For metric spaces $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \win \menGame{X}$
        \item $F \markwin \menGame{X}$
      \end{enumerate}
  \end{cor}

  \begin{ex}
  Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed. This space is a non-regular example where $F \win \menGame{R}$, but $F \not\markwin \menGame{R}$, that is, $R$ is not $\sigma$-(relatively compact).
  \end{ex}

@@

  We define a new property ``\scish'' to describe a sufficient condition for $F \kmarkwin{2}\menGame{X}$.

  \begin{defn}
    Let $\mc U$ be a cover of $X$. We say $C\subseteq X$ is $\mc U$-compact if there exists a finite subcover of $\mc U$ which covers $C$.

    We say $X$ is \scish~if there exist functions $r_{\mc V}:X\to\omega$ for each open cover $\mc V$ of $X$ such that both of the following sets are $\mc V$-compact for all open covers $\mc U$, $\mc V$ and $n<\omega$:
      \[
        c(\mc V,n)=\{ x\in X : r_{\mc V}(x)\leq n\}
      \]
      \[
        p(\mc U,\mc V)=\{ x\in X : 0<r_{\mc U}(x)<r_{\mc V}(x)\}
      \]
  \end{defn}

  \begin{defn}
    For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$. If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\alcomp g$).
  \end{defn}

  \begin{lem}\label{kunlem}
    For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \alcomp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals. In addition, the range of each $f_\alpha$ is co-infinite.
  \end{lem}

@@

  \begin{thm}
    If $X$ is \scish, then $F \kmarkwin{2}\menGame{X}$.
  \end{thm}

@@

  \begin{cor}
    $F\kmarkwin{2}\menGame{\oneptlind{\omega_1}}$
  \end{cor}

  \begin{defn}
    The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\alcomp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
  \end{defn}

  \begin{prop}
    $\neg S(\kappa,\omega,\omega)$ for $\kappa>2^\omega$
  \end{prop}

@@

  \begin{cor}
    $S(\kappa,\omega,\omega)$ implies $F\kmarkwin{2}\menGame{\oneptlind{\kappa}}$.
  \end{cor}

  \begin{defn}
    A finite partial function $p$ from $A$ to $B$ has a domain which is a finite subset of $A$ and a range which is a finite subset of $B$. Let the set of all finite partial functions from $A$ to $B$ be denoted by $Fn(A,B)$.

    Then let $Fn^2(\mc A,B)\subset Fn(\mc A,Fn(\bigcup \mc A,B))$ such that for each $p\in Fn^2(\mc A,B)$, $p(A)=p_A\in Fn(A,B)$.
  \end{defn}

  \begin{defn}
    Let $\pok\subset Fn^2([\kappa]^\omega,\omega)$ be such that each $p_A$ is injective, and give it the partial order $\leq$ defined by $q\leq p$ if and only if:
          \begin{itemize}
            \item $\dom(q)\supseteq\dom(p)$
            \item For each $A\in\dom(p)$, $q_A\supseteq p_A$
            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$. That is, for $\alpha\in A\cap B$
              \[
                \alpha\in\dom(q_A)\setminus(\dom(p_A)\cup\dom(p_B))
                \Rightarrow
                \alpha\in\dom(q_B) \text{ and } q_A(x)=q_B(x)
              \]
          \end{itemize}
  \end{defn}

  \begin{lem}
    $\pok$ has property $K$ (and thus is c.c.c.). That is, let $P\subseteq\pok$ be uncountable: there is an uncountable $Q\subseteq P$ such that points in $Q$ are pairwise compatible.
  \end{lem}

@@

  \begin{cor}
    For each $\kappa$, $F\kmarkwin{2}\menGame{\oneptlind{\kappa}}$ is consistent with ZFC.
  \end{cor}

@@

  Besides various limited information characterizations of $\menGame{X}$, there are other interesting covering properties between $\sigma$-(relatively compact) and Menger.

  \begin{defn}
    A colleciton of subsets of a space $X$ is (\textbf{really}) \textbf{ample} if has a finite subcover for each (relatively) compact subset of $X$.
  \end{defn}

  \begin{prop}
    Every ample cover of a regular space $X$ is really ample.
  \end{prop}

@@

  \begin{ex}
    Let the real numbers $R$ be given the topology generated by open intervals with countable sets removed. $R$ is not relatively Alster and $F\win\menGame{R}$. If $S(2^\omega,\omega,\omega)$ holds, then $F\kmarkwin{2}\menGame{R}$.
  \end{ex}

@@

    It was proven earlier that $F\win\menGame{R}$. Assuming $S(2^\omega,\omega,\omega)$, we construct a $2$-Mark\"ov strategy by first defining the following:
      \begin{itemize}
        \item Let $z_n$ enumerate the integers for $n<\omega$.
        \item For each open cover $\mc V$ of $R$, let $A(\mc V)$ be a countable set such that $[z_n,z_n+1)\setminus A(V)$ is $\mc V$-compact for each $n<\omega$.
        \item Let $f_A:A\to\omega$ for $A\subseteq R$ witness $S(2^\omega,\omega,\omega)$.
      \end{itemize}

@@

  \begin{defn}
    A space $X$ is \textbf{Hurewicz} if for each sequence of open covers $\mc U_n$, there are $\mc F_n \in [\mc U_n]^{<\omega}$ such that $X=\bigcup_{m<\omega}\bigcap_{m\leq n<\omega}\cup\mc F_n$.
  \end{defn}

@@

  \begin{defn}
    The \textbf{filling game} $\cloFillGame{J}$ on an ideal $J$ proceeds as follows: player $M$ chooses $M_0 \in \<J\>$, the $\sigma$-completion of $J$, in the initial round, followed by $N$ choosing $N_0\in J$. In round $n+1$, player $M$ chooses $M_{n+1}$ where $M_n\subseteq M_{n+1}\in\<J\>$, and player $N$ replies with $N_{n+1}\in J$. Player $N$ wins the game if $\bigcup_{n<\omega} N_n \supseteq \bigcup_{n<\omega} M_n$. (The sets in $J$ and $\<J\>$ are thought of as nowhere-dense and meager sets, respectively.)

    The \textbf{strict filling game} $\sfillgame{J}$ proceeds analogously, with the added requirement that $M_n\subsetneq M_{n+1}$. This game has been studied by Scheepers.
  \end{defn}

  \begin{thm}
    $N\ktactwin{2}\sfillgame{J} \Rightarrow N\kmarkwin{2}\cloFillGame{J}$
  \end{thm}

@@

    We define a $2$-Markov strategy $\tau$ for $F$ in $\cloFillGame{\kappa}$ as follows:

@@

  \begin{ex}
    There is a free ideal $J$ such that $N\not\ktactwin{2}\sfillgame{J}$ but $N\kmarkwin{2}\cloFillGame{J}$.
  \end{ex}

@@

    Certainly, if $J$ is the collection of nowhere dense subsets of $A\cup V$, then $F\kmarkwin{2}\cloFillGame{J}$. In fact, since $A\cup V$ is meager, $F\prewin\cloFillGame{J}$.
